Data Preparation

### 2019-01-11 Data Preparation.Rmd

Our dataframe contains many variables that are either empty or meaningless for our analysis, thus we select ony the 10 variables that we will use for the anlysis, and give them more comprehensible names.

```{r}
d_transcript <- d_transcript %>%
  filter(`Appraisal (Description)` == "Grade supervisor") %>%
  select(`Student Number`, `Module (Abbrev.)`, `Module (Desc.)`,
         `Program (Description)`, `Academic Year`, `Academic Session`,
         `Number rep. attemp`, `Grade symbol`, `Booking Status (Desc.)`) %>%
  rename(`Student ID Number` = `Student Number`,
         `Course Code` = `Module (Abbrev.)`,
         `Course Title` = `Module (Desc.)`,
         `Study Program` = `Program (Description)`,
         `Civil Year` = `Academic Year`, # double check
         `Period` = `Academic Session`,
         `Number Repeated Attempt` = `Number rep. attemp`,
         Grade = `Grade symbol`,
         `Status` = `Booking Status (Desc.)`) %>% # is there a better name for the variable?
  distinct
```

Each faculty had a different code for their calendars, we want to standardise them so we can compare. We convert everything into UCM calendar codes and save it under a variable `Period`:
```{r}
d_transcript <- d_transcript %>%
  mutate(Period = case_when(Period == 1 ~ "1 to 6"  ,
                            Period == 2 ~ "1 to 3"  ,
                            Period == 3 ~ "4 to 6"  ,
                            Period == 680 ~ "5"     , # exception
                            Period == 350 ~ "3 to 5", # exception
                            Period == 403 ~ "4 to 5", # exception
                            Period == 900 ~ "1 to 6", # exception
                            between(Period, 100, 199) ~ "1",
                            between(Period, 200, 299) ~ "2",
                            between(Period, 300, 399) ~ "3",
                            between(Period, 400, 499) ~ "4",
                            between(Period, 500, 599) ~ "5",
                            between(Period, 600, 660) ~ "6",
                            between(Period, 901, 999) ~ "1"))

```
###Dropping useless variables:
Now that our `Period` variable is clean, we can exclude the variables that we will not use, and we will delete newly generated duplicate rows:

```
###Extracting grades
We notice that there are several values under `Grade` for the same course. We are interested in keeping only the final grades, corresponding to the rows where `Appraisal Title` is marked as "Grade supervisor". 
So lets extract the grades and add the course concentration by keeping the first three letters of the `Code`:

@@

# Save Data

```{r}
save(lists, d_course, d_AoD, d_assessment, d_transcript,
     file = "data_pillar_1.RDATA")
save(lists, d_course, d_AoD, d_assessment, d_transcript,
     d_overview, d_description, d_manual,
     file = "data_pillar_2.RDATA")
```

>>>>

Our dataframe contains many variables and rows that are either empty or meaningless for our analysis. First, we filter, the final grades of studets to keep only relevant rows (Final Confirmed Grades are those with `Appraisal (Description)` as "Grade supervisor"). Then we select ony the 10 variables that we will use for the anlysis, and give them more comprehensible names.
```{r}
d_transcript <- d_transcript %>%
  filter(`Appraisal (Description)` == "Grade supervisor") %>%
  select(`Student Number`, `Module (Abbrev.)`, `Module (Desc.)`,
         `Program (Description)`, `Academic Year`, `Academic Session`,
         `Number rep. attemp`, `Grade symbol`, `Booking Status (Desc.)`) %>%
  rename(`Student ID Number` = `Student Number`,
         `Course Code` = `Module (Abbrev.)`,
         `Course Title` = `Module (Desc.)`,
         `Study Program` = `Program (Description)`,
         `Civil Year` = `Academic Year`, # double check
         `Period` = `Academic Session`,
         `Number Repeated Attempt` = `Number rep. attemp`,
         Grade = `Grade symbol`,
         `Status` = `Booking Status (Desc.)`) %>% # is there a better name for the variable?
  distinct
```

Each faculty had a different code for their calendars, we want to standardise them so we can compare. We convert everything into UCM calendar codes (the correspondance between calendars was given to us by R. Vos) and save it under a variable `Period`:
```{r}
d_transcript <- d_transcript %>%
  mutate(Period = case_when(Period == 1 ~ "1 to 6"  ,
                            Period == 2 ~ "1 to 3"  ,
                            Period == 3 ~ "4 to 6"  ,
                            Period == 680 ~ "5"     , # exception
                            Period == 350 ~ "3 to 5", # exception
                            Period == 403 ~ "4 to 5", # exception
                            Period == 900 ~ "1 to 6", # exception
                            between(Period, 100, 199) ~ "1",
                            between(Period, 200, 299) ~ "2",
                            between(Period, 300, 399) ~ "3",
                            between(Period, 400, 499) ~ "4",
                            between(Period, 500, 599) ~ "5",
                            between(Period, 600, 660) ~ "6",
                            between(Period, 901, 999) ~ "1"))

@@

# Save Data
```{r}
save(lists, d_course, d_AoD, d_assessment, d_transcript,
     file = "data_pillar_1.RDATA")
save(lists, d_course, d_AoD, d_assessment, d_transcript,
     d_overview, d_description, d_manual,
     file = "data_pillar_2.RDATA")
```
